---
title: "p8105_hw5_bh2852"
author: "Beicheng Huang"
date: "2023-11-16"
output: github_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(ggplot2)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

### Problem 0

```{r load_libraries}
library(tidyverse)
```



##Quesetion 2


```{r create dataframe and function}

data_col = tibble(filename = list.files("./data/"))

read_all = function(csv, path = "./data/") {
  paste(path, csv, sep = "/") |> 
  read.csv()
}


long_study =  
  data_col |> 
  mutate(nested_data = map(data_col$filename, read_all)) |> 
  unnest(nested_data) |> 
  mutate(arm_subject = map_chr(.x = filename, ~ unlist(str_split(.x, "\\.") ) [[1]] )) |> 
  mutate(arm = map_chr(.x = arm_subject, ~ unlist(str_split(.x, "_") ) [[1]] )) |> 
  mutate(subject_id = map_chr(.x = arm_subject, ~ unlist(str_split(.x, "_") ) [[2]] )) |> 
  select(-filename, -arm_subject)
```


```{r tidying and plotting}
pivot_longer = 
  long_study |> 
  pivot_longer(week_1:week_8,
               names_to = "week",
               names_prefix = "week_", #removes the week prefix
               values_to = "value") |> 
  mutate(week = as.integer(week))

spaghetti_plot = 
  pivot_longer |> 
  ggplot(aes(week, value, color = subject_id)) + 
  geom_line() + 
  facet_wrap(~arm) + 
  labs(x = 'Week', y = 'Value', title = 'Spaghetti Plot', color = "Subject ID")

spaghetti_plot
```

##Q3


```{r Set Parameters}
set.seed(114)

n <- 30
sigma <- 5
alpha <- 0.05
mius <- c(0, 1, 2, 3, 4, 5, 6)

```


```{r Define functions for miu and sigma}
sim_mean_sd = function(n = 30, miu, sigma = 5) {
  simulation = tibble(
    x = rnorm(n, mean = miu, sd = sigma),
  )
  
  simulation |> 
    summarize(
      miu_hat = mean(x),
      sigma_hat = sd(x)
    )
}
```


```{r Define a function for the t-test and simulation}
perform_t_test <- function(n, miu, sigma) {
  sample <- rnorm(n, mean = miu, sd = sigma)
  test_result <- t.test(sample, miu = 0)
  broom::tidy(test_result)
}
```


```{r Initialize data frame to store results}
results <- tibble(miu = numeric(), miu_hat = numeric(), p_value = numeric(), reject = logical())
```


```{r Simulation loop}
for (miu in mius) {
  for (i in 1:5000) {
    sim_results <- sim_mean_sd(n, miu, sigma)
    t_test_results <- perform_t_test(n, miu, sigma)
    results <- results |> 
      add_row(miu = miu, 
              miu_hat = sim_results$miu_hat, 
              p_value = t_test_results$p.value, 
              reject = t_test_results$p.value < alpha)
  }
}
```


```{r Power data for plot 1}
power_results <- results |> 
  group_by(miu) |> 
  summarise(power = mean(reject))
```


```{r Plot1}
power_results |> 
  ggplot(aes(x = miu, y = power)) +
  geom_point() +
  geom_line() +
  labs(title = "Power vs. True Mean", x = "True Mean (miu)", y = "Power")
```
This graph shows the relation between the proportion of times that null was rejected on the y axis and true mean of μ on the x axis. As the true mean increases, the proportion of times that null will be rejected increases, thus the power of the test increases and approaches 1. This means that the larger the true means, the easier to reject the null hypothesis, thus having greater power.


```{r}
estimates_data <-
  results |> 
  group_by(miu) |> 
  summarize(avg_miu_hat = mean(miu_hat))

estimates_rejection_df =
  results |> 
  mutate(decision = ifelse(p_value < 0.05, "reject", "fail to reject")) |> 
  filter(decision == "reject") |> 
  group_by(miu, decision) |> 
  summarize(avg_miu_hat_rejected = mean(miu_hat))
```

```{r Plot2 average estimate miu_hat vs miu}
estimates_data |> 
  ggplot(aes(x = miu)) +
  geom_point(aes(y = avg_miu_hat, color = "Average Estimate of μ"), shape = 1) +  
  geom_line(aes(y = avg_miu_hat, color = "Average Estimate of μ")) +
  geom_point(data = estimates_rejection_df, aes(y = avg_miu_hat_rejected, color = "Rejected Average Estimate of μ"), shape = 2) +
  geom_line(data = estimates_rejection_df, aes(y = avg_miu_hat_rejected, color = "Rejected Average Estimate of μ"), linetype = "dashed") +
  labs(
    title = "Average Estimated Mean vs. True Mean",
    x = "True Mean (miu)",
    y = "Average Estimated Mean",
    color = "miu_hat"
  ) +
  scale_color_manual(
    values = c("Average Estimate of μ" = "darkgreen", "Rejected Average Estimate of μ" = "red")
  ) 
```
